Language-Parametric Techniques for Live Probes

### 2023-07-25 paper/paper.tex
tweaks

The question left unanswered in Victor's presentation is: how to build such live probes? While there has been recent research showcasing an implementation approach~\cite{ExampleBasedGraal}, it depends on specific a runtime system (GraalVM), and cannot be easily transferred to other languages. So a more specific question is: how to  engineer live probes without dedicated compiler or runtime support?

>>>>

The question left unanswered in Victor's presentation is: how to build such live probes? While there has been recent research showcasing implementation approaches~\cite{ExampleBasedGraal}, they depends on a specific runtime system (e.g., GraalVM), or language specific ``hacks''~\cite{LiveLit}, and hence cannot be easily transferred to other languages. So a more specific question is: how to  engineer live probes \textit{generically}, without dedicated compiler or runtime support?
